Moving Together

### 2023-01-18 graphs_newt_snakes/move_together.Rmd
I have updated the results for the last set of experiments. Tomorrow I will need to spend some time reviewing them.

>>>>

```{r, finding the slope of coevolution}

newt_first_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$Newt_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$group_rep), FUN=mean), c("group_rep", "Nstart" ))

snake_first_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$Snake_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=100 & move_together_lit$generation<=1000),]$group_rep), FUN=mean) , c("group_rep", "Sstart" ))

newt_last_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$Newt_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$group_rep), FUN=mean), c("group_rep", "Nend" ))

snake_last_mean_pheno = setNames(aggregate(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$Snake_mean_Pheno, list(move_together_lit[which(move_together_lit$generation>=(max(move_together_lit$generation)-1000) & move_together_lit$generation<=max(move_together_lit$generation)),]$group_rep), FUN=mean), c("group_rep", "Send" ))

mean_phenotype_of_group = cbind(newt_first_mean_pheno, newt_last_mean_pheno[2], snake_first_mean_pheno[2], snake_last_mean_pheno[2])

move_together_lit$Nstart = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"Nstart"]

move_together_lit$Sstart = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"Sstart"]

move_together_lit$Nend = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"Nend"]

move_together_lit$Send = mean_phenotype_of_group[match(move_together_lit$group_rep, mean_phenotype_of_group$group_rep),"Send"]

genstart_newt = setNames(aggregate(move_together_lit[which(move_together_lit$Newt_mean_Pheno<=(move_together_lit$Nstart)) ,]$generation, list(move_together_lit[which(move_together_lit$Newt_mean_Pheno<=(move_together_lit$Nstart)),]$group_rep), FUN=max), c("group_rep", "Nstr_gen"))

genstart_snake = setNames(aggregate(move_together_lit[which(move_together_lit$Snake_mean_Pheno<=(move_together_lit$Sstart)) ,]$generation, list(move_together_lit[which(move_together_lit$Snake_mean_Pheno<=(move_together_lit$Sstart)),]$group_rep), FUN=max), c("group_rep", "Sstr_gen"))

move_together_lit$Nstr_gen <- genstart_newt[match(move_together_lit$group_rep, genstart_newt$group_rep),'Nstr_gen']
move_together_lit$Sstr_gen <- genstart_snake[match(move_together_lit$group_rep, genstart_snake$group_rep),'Sstr_gen']

genend_newt = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(move_together_lit$Nend)) ,]$generation, list(move_together_lit[which( move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(move_together_lit$Nend)),]$group_rep), FUN=min)

genend_snake = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(move_together_lit$Send)) ,]$generation, list(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(move_together_lit$Send)),]$group_rep), FUN=min)

move_together_lit$genend_newt <- genend_newt[match(move_together_lit$group_rep, genend_newt$Group.1),'x']
move_together_lit$genend_snake <- genend_snake[match(move_together_lit$group_rep, genend_snake$Group.1),'x']

# get the difference in generation time and the difference in phenotype

```{r, making newts and snakes in grid form}

duo_grid_plot<- function(file_name, spegen, file, type, row_num, col_num){

main_plot<-ggplot(data_long_type_comp, aes(x = x_loc, y = y_loc))+
  geom_tile(aes(fill = as.numeric(measurement)))+
  facet_wrap(~species)+

  theme_bw()+
  theme(legend.justification = "top")

final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)

return(final_plot)}
